### 2017-09-30 TF-vldb2018/subsec-Ginc.tex

%\vspace{0.5ex}
\stitle{Remarks}. Note that (a) the running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$, and
(b) the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
From these, we complete the proof of Theorem~\ref{thm-framework-inc}.

>>>>

%\vspace{0.5ex}
\stitle{Remark}. Note that the running time of \incp and \incd is determined by \{$P, \Delta P, \tilde{M}(P,G)$, $\affballsx$\} 
and \{$P, \tilde{M}(P,G)$, $\affballsx$\}, respectively, not directly depending on $G$.
From this, we complete the proof of Theorem~\ref{thm-framework-inc}.
